\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,%
            left=.75in,right=.75in,top=1in,bottom=1in]{geometry}
\setlength{\headsep}{0.25in}

\usepackage{amsthm}

\usepackage{graphicx}
\usepackage{pgfplots}
            
\usepackage[english]{babel}

\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{case}{Case}

\newcommand\restr[2]{{% we make the whole thing an ordinary symbol
  \left.\kern-\nulldelimiterspace % automatically resize the bar with \right
  #1 % the function
  \vphantom{\big|} % pretend it's a little taller at normal size
  \right|_{#2} % this is the delimiter
  }}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}

\usepackage{mathtools}
\DeclarePairedDelimiter\bra{\langle}{\rvert}
\DeclarePairedDelimiter\ket{\lvert}{\rangle}
\DeclarePairedDelimiterX\braket[2]{\langle}{\rangle}{#1 \delimsize\vert #2}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fancyhdr}

\DeclareMathOperator{\interior}{int}

\newcommand{\Tau}{\mathcal{T}}

\newenvironment{amatrix}[1]{%
  \left(\begin{array}{@{}*{#1}{c}|c@{}}
}{%
  \end{array}\right)
}

\usepackage{calligra}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\DeclareFontShape{T1}{calligra}{m}{n}{<->s*[2.2]callig15}{}

\newcommand{\scripty}[1]{\ensuremath{\mathcalligra{#1}}}

\pagestyle{fancy}
\author{Jeremiah Givens}
\newcommand{\subject}{Metric Spaces}
\newcommand{\Date}{9/2/2021} 
\makeatletter
\rhead{{\small\@author}}
\lhead{{\small\subject}}
\chead{{\large Picard's Existence and Uniqueness Theorem}}
\cfoot{}
\rfoot{\thepage}
\lfoot{\today}

\renewcommand{\theequation}{\arabic{equation}}

\begin{document}

\section*{Supporting Lemmas}
\begin{lemma}
Let $x: [a, b] \to \mathbb{R}$ be continuous. Then, $x$ is bounded, and $x$ achieves it's maximum.
\end{lemma}

\begin{lemma}
Let $C$ equal the set of all continuous real-valued functions on the closed interval $[a, b]$. Then, $C$ forms a metric space with the metric $d$ defined by
\begin{align*}
d(x, y) = \max_{t \in [a, b]} |x(t) - y(t)|.
\end{align*}
\end{lemma}


\begin{lemma}
The metric space $(C, d)$ from the previous lemma is complete.
\end{lemma}

\begin{lemma}
Let $x_0 \in \mathbb{R}$, and let $c \in (0, \infty)$. Let $\tilde{C}$ be a subspace of the metric space from Lemma 1, consisting of all functions $x \in C$ such that 
\begin{align*}
d(x, x_0) \leq c.
\end{align*}
Then, $\tilde{C}$ is closed.
\end{lemma}

\begin{lemma}
Let $C$ be a complete metric space. Let $A \subseteq C$ be closed. Then, $A$ is complete.
\end{lemma}

\section*{Main Topic}
The focus of this paper is on solutions to explicit ordinary differential equations of the form
\begin{align}
x' = f(t, x)
\end{align}
where $x: \mathbb{R} \to \mathbb{R}$, $f: \mathbb{R} \times \mathbb{R} \to \mathbb{R}$, and the prime denotes differentiation of $x$ with respect to $t$.  Specifically, we are interested in initial value problems, where
\begin{align*}
x(t_0) = x_0.
\end{align*}

\begin{theorem}
Let $f$ be continuous on a rectangle 
\begin{align*}
R = \{(t, x) \mathbb \in {R}^2 : |t - t_0| \leq a \land |x - x_0| \leq b \},
\end{align*}
and thus bounded on $R$, say
\begin{align}
|f(t, x)| \leq c, \text{ for all } (t, x) \in R.
\end{align}
Suppose $f$ satisfies a Lipschitz condition on $R$ with respect to it's second argument, that is, there is a constant $k$ (Lipschitz constant) such that for $(t, x), (t, v) \in R$
\begin{align}
|f(t, x) - f(t, v)| \leq k |x - v|.
\end{align}
Then the initial value problem (1) has a unique solution. This solution exists on an interval $[t_0 - \beta, t_0 + \beta]$ where 
\begin{align}
\beta < \min \Bigg \{a, \frac{b}{c}, \frac{1}{k} \Bigg \}
\end{align}
\end{theorem}
\end{document}

